\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}

\title{My Use Cases Project}
\author{Dream Builders Group: Nathan Trowers , Mohammad Reza Raeisy, Sahil Vashisht, Nishant Singh }
\date{June 27 2019}

\begin{document}

\maketitle

USE CASE NAME

\section{Create project charter} 

    \subsection{Goal}To provide the User (who is a Project Manager) with (UI / Screen) to Describe the Project Carter. The Project Charter should stored in the system in a Data Format which easily allows it to be parsed / converted in the Statement of Work and / or WBS.
    

    \subsection{Actors}The Project Manager(user) 

    \subsection{Scenario}The system presents a blank statement of work template for the user to enter information under the headings “Functional Requirements” and “Nonfunctional Requirements”.  
The project charter will be shown on a display screen which will be in simple table format .

    Prerequisite: None



\section{Create Planning Documents}

    \subsection{Goal}To display the necessary documents that provide the user with a clear picture of how everything is planned.(Cost planning document,Quality planning documents)
    
    \subsection{Actors}The actors in Planning Documents are executive officers/clients which in this case is user.
    
    \subsection{Scenario}
    \paragraph{1) }The system will present the user with planning document templates to choose from(time planning, cost planning, risk management document, HR skilling requirements) .

    \paragraph{2)} The information saved to the machine’s local disk is viewable as received by the user.
    Prerequisite: The Project Charter data must be available for referencing




\section{Create WBS}

     \subsection{Goal} The goal of this Use Case is to provide The PM who is using our system with a screen to decompose the SOW into a series of small discrete steps. It would be optimal if the System could maintain a LINK of each WBS Step back to the text into SOW.

   \subsection{Actors}  The WBS will be handled by the Human Resource Managers by which every individual can do one task at a time to reduce the time used. 


     \subsection{Scenario} 
The System will provide the USER (which the PM using our system) with a SCREEN to enter details 
The WBS will give every employee the tasks which needs to be done by them based on their work schedule that will be shown on a calender screen


    \paragraph{} Prerequisite: The Project Charter(SOW part), and the employee information will be used to assign the work.



\newpage
\title{UML Diagrams}
\hline
\subsection{Class Name}
    \item createProjectCharter
\subsection{Attributes}
    \item projectCharter:String[]
\subsection{Methods}
    \item createProjChar()
        \item insertS()\\

\subsection{Class Name}
    \item createPlanningDocuments
\subsection{ Attributes}
    \item costPlanningTemplate: String []
    \item qualityPlanningTemplate: String[]
\subsection{Methods}
    \item templateCreate()
    \item templateUse()\\

\subsection{Class Name}
    \item createWBS
\subsection{Attributes}
    \item mainTask[]
    \item (inside level)subsection[]
\subsection{Methods}
    \item breakDownTaks()
    \item insertTask()

\end{document}
